---
output:
  word_document: default
  html_document: default
---
# Name: Israt Jahan Tumpa
# Module 1: Assignment 2

```{r}
library(tidyverse)
```

```{r}
nrow(diamonds)
```

# Question 1 How many rows are in the dataset?
```{r}
diamonddata = diamonds
```
#Question 2 How many columns columns are in the "diamonds" dataset? 

#Question 3 Using ggplot, create a scatterplot of caret (x axis) versus price (y axis). Which statement best describes the relationship between “caret” and “price”?
```{r}
ggplot(diamonddata, aes(x = carat, y = price)) + geom_point() + theme_bw()
```

# Question 4 Repeat Question 3, but in this plot color the scatterplot points by the “cut” variable. Which statement best describes the relationship between “cut” and “price”?

```{r}
ggplot(diamonddata, aes(x = cut, y = price,  color =x,y)) + geom_point() + theme_bw()
```

# Question 5 Repeat Question 4, but in this plot you should facet by “color”.What does “faceting” do to the plot?

```{r}
ggplot(diamonddata, aes(x = cut, y = price,color =x,y )) + geom_point()  +
facet_grid(. ~ color)
```
# Question 6 In the “inventory” data frame that you have just created, what type of variable is “Supplier”?

```{r}
InventoryData <- read_csv("InventoryData.csv")
View(InventoryData)
```
```{r}
InventoryData <- read_csv("InventoryData.csv")
inventory <- data.frame(InventoryData)
view(inventory)
```
# Question 7 In the “inventory” data frame that you have just created, what is the mean of the “On Hand” variable?
```{r}
mean_value <- mean(inventory$`On.Hand`)
```
# Question 8 Use a filter to create a new data frame called “inventoryA” containing only inventory from Supplier A. How many rows are in this new data frame?

```{r}
inventoryA <- filter(inventory, Supplier == "A")
```

# Question 9
```{r}
inventoryA <- mutate(inventoryA, OnHandRatio = On.Hand/Annual.Demand)
```
# Question 10 Using the “inventoryA” object that you created in Question 9, create a new data frame called “avg_cost” that contains the average “Cost per Unit ($)” by each “Item SKU” (let this quantity be in a variable called “SKUAvgCost. Hint: Recall the summarize and group_by functions and the use of the backtick character from Task 8. Your data frame should have only two columns:”Item SKU” and “SKUAvgCost”. What is the “SKUAvgCost” of items with an “Item SKU” of 011?

```{r}
avg_cost <- inventoryA %>%
  group_by(`Item.SKU`) %>%
  summarize(SKUAvgCost = mean(Cost.per.Unit....))

SKUAvgCost_011 <- avg_cost %>%
  filter(`Item.SKU` == "011")
```


