---
output:
  word_document: default
  html_document: default
---
---
title: "Assignment_Model Validation"

```{r}
library(tidyverse)
library(lubridate)
library(tidymodels)
library(dplyr)
```

```{r}
bike_cleaned_4 <- read_csv("bike_cleaned-4.csv")
View(bike_cleaned_4)
```

```{r}
bike = bike_cleaned_4
summary(bike)
```

# Convert “dteday” from a character variable to a date variable. The code below will perform this conversion:
```{r}
bike = bike %>% mutate(dteday=mdy(dteday))
summary(bike)
```

```{r}
 bike = bike %>% mutate_if(is.character, as_factor)
bike = bike %>% mutate(hr = as_factor(hr))
```

# Question 1: Split the data into training and testing sets. Your training set should have 70% of the data. Use a random number (set.seed) of 1234. Your split should be stratified by the “count” variable.

```{r}
set.seed(1234)
bike_split = initial_split(bike, prop = 0.70, strata = count)
train = training(bike_split)
test = testing(bike_split)
```

# Question 3: Build a linear regression model (using the training set) to predict “count” using the variables “season”, “mnth”, “hr”, “holiday”, and “weekday”, “temp”, and “weathersit”
```{r}
bike_recipe = recipe(count ~ season + mnth + hr + holiday + weekday + temp + weathersit, train)

lm_model = 
  linear_reg() %>%
  set_engine("lm")

lm_wflow =
  workflow() %>%
  add_model(lm_model) %>%
  add_recipe(bike_recipe)

lm_fit = fit(lm_wflow, train)
```

```{r}
summary(lm_fit$fit$fit$fit)
```
# Question 5: Determine the performance of your model on the testing set.What is the R-squared value (to four decimal places) of your model on the testing set? REMINDER: DO NOT build a model on the testing set. Use your model that was developed on the training set.
```{r}
lm_fit %>% predict(test) %>% bind_cols(test) %>% metrics(truth = count, estimate = .pred)
```
```{r}

```

