
title: "Clustering Assignment"

```{r}
library(tidyverse)
library(tidymodels)
library(cluster)
library(factoextra)
library(dendextend)
```

```{r}
library(readr)
trucks_1 <- read_csv("trucks-1.csv")
View(trucks_1)
```

```{r}
trucks = trucks_1
summary(trucks)
```
# Question 1: Plot the relationship between Distance and Speeding.

```{r}
ggplot(trucks, aes(x=Distance,y=Speeding)) + geom_point() + theme_bw() +
geom_smooth(method ="lm", se=FALSE, color="red") + theme_bw()
```
# Question 2: Create a new data frame called “trucks_cleaned” that contains the scaled and centered variables. Two notes: 1) The “predictor” variables in the recipe are “Distance” and “Speeding” and 2) There is no need to create dummy variables as there are no categorical variables in the data. Be sure that you do NOT include the Driver_ID variable.
#What is the maximum value (to four decimal places) of the Distance variable in the scaled dataset?
```{r}
trucks_cleaned = trucks %>% select(-Driver_ID) 
str(trucks_cleaned)
view(trucks_cleaned)
summary(trucks_cleaned)
```

```{r}
kmeans_recipe = recipe(~Distance + Speeding,trucks_cleaned)

trucks_cleaned_dummy = kmeans_recipe %>%
  step_scale(all_numeric()) %>%
  step_center(all_numeric())

trucks_cleaned_dummy = prep(trucks_cleaned_dummy, trucks_cleaned)

turcks_cleaned = bake(trucks_dummy, trucks_cleaned)
```

```{r}
summary(trucks_cleaned)
```
# Question 3 Use k-Means clustering with two clusters (k=2) to cluster the “trucks_cleaned” data frame. Use a random number seed of 64. Use augment to add the resulting clusters object to the the “trucks” data frame. Design an appropriate visualization to visualize the clusters.

```{r}
set.seed(64)
clusts =
  tibble(k = 2) %>%
  mutate(
  kclust = map(k, ~kmeans(trucks_cleaned, .x)),
  tidied = map(kclust, tidy),
  glanced = map(kclust, glance),
  augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```

```{r}
cust_clust = kmeans(trucks_cleaned, centers = 2)
cust_clust
```
```{r}
trucks_cleaned = augment(cust_clust,trucks)
head(trucks_cleaned)
```

# Question 4: Create a visualization to show how the clusters appear from values of k from 1 to 8. Use a random number seed of 412. Which value of k appears to be most appropriate for this data?
```{r}
set.seed(412)
clusts =
  tibble(k = 1:8) %>%
  mutate(
  kclust = map(k, ~kmeans(trucks_cleaned, .x)),
  tidied = map(kclust, tidy),
  glanced = map(kclust, glance),
  augmented = map(kclust, augment, turcks_cleaned)
  )

clusts
```

```{r}
clusters = 
  clusts %>%
  unnest(cols =c(tidied))

assignments =
  clusts %>%
  unnest(cols = c(augmented))

clusterings =
  clusts %>%
  unnest(cols = c(glanced))
```

```{r}
ggplot(clusterings, aes(k, tot.withinss)) +
  geom_line() +
  geom_point() + theme_bw()
```

```{r}
p1 =
  ggplot(assignments, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) +
  facet_wrap(~k)
p1
```
# Question 5: Create a plot of k versus within cluster sum of squares. Hint: We did this in the first clustering lecture. What number of clusters appears to be ideal based on this plot?

```{r}
cust_clust = kmeans(trucks_cleaned, centers = 4)
cust_clust
```

