---
output:
  word_document: default
  html_document: default
---
---
title: "Missing Data"

```{r}
library(tidyverse)
library(VIM)
library(mice)
library(skimr)
library(naniar)
library(UpSetR)
```

```{r}
library(readr)
class_grades <- read_csv("class-grades.csv")
View(class_grades)
```

# Task 1:For which variables is there missing data?

```{r}
str(class_grades)
summary(class_grades)
skim(class_grades)
```

#Task 2:Use the VIM package to visualize missingness. Are there any students that are missing multiplepieces of data?

```{r}
gg_miss_var(class_grades)
vis_miss(class_grades)
```

#Task 3:Use row-wise deletion of missing values to create a new data frame. How many rows remain in this data frame?

```{r}
class_gradesrowdel = class_grades %>% drop_na()
skim(class_gradesrowdel)
```

# Task 4: Use column-wise deletion of missing values to create a new data frame (from the original data frame not from the data frame created in Task 3). How many columns remain in this data frame?

```{r}
class_gradescoldel = class_grades %>% select(- Tutorial, -Midterm, -TakeHome, -Final)
vim_plot = aggr(class_gradescoldel, numbers = TRUE, prop = c(TRUE, FALSE), cex.axis=.7)
skim(class_gradescoldel)
```
# Task 6 Use the “mice” package to impute the missing data in this dataset. Set “m = 5” and “method =”pmm"" in the imputation. You MUST use a random number seed of 123 for this imputation. What is the mean value for the “Final” variable after imputation?

```{r}
set.seed(123)
imp_Final =mice(class_grades, m=5, method = 'pmm' , printFlag = FALSE)
summary(imp_Final)
```
```{r}
class_grades_complete = complete(imp_Final)
summary(class_grades_complete)
```

