---
title: "Assignment-2_Simple Linear Regression"
output: html_document
date: "2023-09-08"
---
Libraries
```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)
```
# Question 1 How many rows are in the “air” dataframe?
#Question 2 How many columns are in the “air” dataframe?
```{r}
air = airquality
```

```{r}
str(airquality)
```
# Question 4 Which variable is most likely to be the response (Y) variable?
```{r}
ggpairs(air) 
```
# Question 5 How many rows remain in this new (air2) data frame?
# Question 6 How many columns remain in this new (air2) data frame?
```{r}
air2 = air %>% drop_na()
```
# Use the “ggpairs” function to develop a visualization of the relationships in this dataset and to show correlation values for the combinations of variables.
```{r}
ggpairs(air2)
```
# Question 7 Which variable is most strongly correlated with the “Ozone” variable?
# Question 8 Which variable is least strongly correlated with the “Ozone” variable?
```{r}
ggcorr(air2, label = TRUE)
```
# Question 9 Plot “Temp” (x axis) versus “Ozone” (y axis) using the “ggplot” function. Choose an appropriate chart type. Which statement best describes the relationship between “Temp” and “Ozone”?

```{r}
ggplot(air2, aes(x=Temp ,y=Ozone)) + geom_point() + theme_bw() +
geom_smooth(method ="lm", se=FALSE, color="red") + theme_bw()
```
# Use Tidymodels to create a linear regression model using “Temp” to predict “Ozone”. You miss wish to call your model fit “lm_fit”.
# Question 10 What is the slope of this regression model (to four decimal places)?
# Question 11 what is the R-squared value of this model (not Adjusted R-squared) (to three decimal places)?
# Question 12 Is the “Temp” variables significant in the model?
```{r}
air_2_simple = recipe(Ozone ~ Temp, air2)

lm_model = 
  linear_reg() %>%
  set_engine("lm")

lm_wflow =
  workflow() %>%
  add_model(lm_model) %>%
  add_recipe(air_2_simple)

lm_fit = fit(lm_wflow, air2)
```

```{r}
summary(lm_fit$fit$fit$fit)
```
```{r}
slope <- coef(lm_fit$fit$fit$fit)["Temp"]
```

# Question 13 Use the code below to generate 95% confidence intervals for the coefficients. Note that you may need to change “lm_fit” to the name of your model fit if you used a different name.
```{r}
confint(lm_fit$fit$fit$fit)
```
# Question 14: Using your linear regression model with “Temp” to predict “Ozone”, what is the predicted. “Ozone” value when “Temp” is equal to 80 (to two decimal places)?
```{r}
testdata <-data.frame(
predict(lm_fit, new_data = testdata)
```

